PCA Toolkit

### 2019-11-19 pca-toolkit.Rmd
add slides

>>>>

## Pipeline to compute PCs

```{r, out.width="55%"}
knitr::include_graphics("figures/PCA-pipeline.svg")
```

## Remaining problem: what is really PC16?

## Facts about PC16

- unchanged if we impute randomly (using allele frequencies)

- People with PC16 > 30

    - have 36% correlation between PC16 and number of NAs per individuals (also 13% for PC1, 12% for PC3, 11% for PC13 and 14)

    - from almost all assessment centers (data-field 54), batches (data-field 22000) and plates (data-field 22007)

    - from different ancestries (data-field 21000)

    - have between 0.2% and 3.7% of missing values

- loadings are almost all positives (not symmetric)

## Possible explanation: heterozygosity

```{r, out.width="90%"}
knitr::include_graphics("figures/het-PC16.png")
```

## Possible explanation: heterozygosity

```{r, out.width="90%"}
knitr::include_graphics("figures/het-NA.png")
```
